%*******************************************************
% Acknowledgments
%*******************************************************
%\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{
    \slshape
    %\calligra
    %I need to insert a nice quotation here, \\
    %before printing this dissertation.} \\ \medskip
    %--- Stefano Martina
    I hear and I forget.\\
    I see and I remember.\\
    I do and I understand.} \\ \medskip
    --- Confucius
\end{flushright}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
I would like to express my sincere gratitude to my coordinator
Prof. Alessandra Sestini and my advisor 
Ph.D. Carlotta Giannelli for their patience and the priceless revision
work. I want to thank them also for introducing me to this research
area and for their guidance through the development of this project.

I also would like to thank all the professors for contributing, with
their passion, to make me a better person and for instilling in me the
passion for knowledge. Among them, a special mention goes to
Prof. Pierluigi Crescenzi for the advice that he gave me for
complexity analysis, Prof. Maria Cecilia Verri for the advice on the
algorithms, Prof. Gregorio Landi and Prof. Franco Bagnoli for
introducing me to stochastic methods.

I would like to thank all my friends for being life companions and for
all the adventures that we had and we will continue to have.

A special loving thank goes to my parents Mauro and Rosa, and to my
brother Simone, for patiently 
contributing to sustain me all this years, for tangible and
intangible needs.

Finally, last but not least, I want to thank
Federica, the woman of my life, for making the world a worthier place
to live in 
and for the 
unconditional love that she gives to me everyday (and also for
helping me to make this text more readable).

\begin{flushright}{\calligra
Stefano Martina}
\end{flushright}
\endgroup




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dissertation"
%%% End:
