\documentclass[dissertation.tex]{subfiles}
\begin{document}
\chapter{Introduction}
The design of \emph{motion planning} strategies plays a fundamental
role in different applications, from robotics to scientific
visualization. \emph{Path planning} problem is
more specific, it consists in identifying paths that do not
intersect any obstacle.

In this project we are interested in generating smooth
paths. Smoothness is a desirable property that is
frequently presented in literature for the planar case. Consider, for
instance, the works \cite{maekawa}, \cite{ho-liu}, \cite{li} and
\cite{giannelli}. On in the latter in particular, they used
\acf{PH} curves that have interesting features for the \acf{CAM} field
\cite{farouki}.

In regards of spatial path planning, the smoothing problem is less
covered in literature. For instance, in \cite{hrabar} it is not clear
how a smooth path is obtained from the initial polynomial chain. In
\cite{yang} the smoothness is considered, but the method is not
optimal because it consists in alternating smoothing and
obstacle-checking phases until an admissible solution is
obtained. Other works, like \cite{aghababa} and \cite{kroumov}, use 
stochastic methods to achieve smoothness.

\bs curves are a reference standard in \ac{CAD} and \ac{CAGD}
\cite{hughes}\cite{foley}\cite{farin}\cite{farin2}. Thus, we decide to
develop a 3D path planning application using this kind of curves, as
\cite{yang} do. However, as earlier mentioned,
\cite{yang} uses a \emph{try and check} approach to the curve
smoothing, we present a method that finds a smooth
curve on the first 
attempt instead.

The considered topic is highly cross-disciplinary. In fact we design
this project with the help of an extended set of
competencies acquired during the courses. We apply notions of
\emph{linear algebra} for the collision checks; \emph{numerical
  analysis} for the curves design; \emph{computational
  geometry},
\emph{graph theory}, \emph{probability} and \emph{algorithm theory}
for the algorithms design; and, finally, \emph{theoretical computer
  science} for cost analysis.

We focus on finding a trade-off between having a short curve, a
smooth curve, and keeping the time complexity low.
Different solutions are explored, with different qualitative effects
on the curve.

Regarding the scene representation, different kinds of
polyhedral obstacle are considered.

A framework in Python is developed using \ac{VTK} for the graphic
output. We use a roadmap method based on \acp{VD} to create a
graph (details in
\cref{sec:baseGraph}) that is the base
structure for the project. Using such structure, three
different solutions are presented.
\begin{enumerate}
\item The first method benefits from the \acf{CHP} of \bs
  curves (\cref{sec:convexHull}). A transformation is applied on the
  graph such that every path in it can be used as a control polygon
  for an obstacle-free curve (\cref{sec:trigraph}). Therefore, the
  algorithm selects the shortest path in the transformed graph and
  builds the curve on it (\cref{sec:inter1}).
\item The second method still benefits from the \ac{CHP},
  but it picks the shortest path directly in the base graph. If
  violations of the \ac{CHP} emerge in it, then rectification
  measures are taken (cref{sec:inter2}).
\item The third method uses a probabilistic approach. Starting from
  the shortest path in the original graph, it performs a simulated
  annealing optimization (\cref{sec:simulatedAnnealing}) that converges
  in a state where we have an optimal trade-off between having a short curve,
  and low curvature and torsion peaks (\cref{sec:inter3}).
\end{enumerate}

This document consists of three parts. The first
(\cref{prt:stateOfArt})
is dedicated to the state of the art: we provide a survey of
different topics and algorithms related to \emph{motion planning}.

The
second part (\cref{prt:project}) is committed to describing
all the different parts of the algorithm. In details:
\begin{itemize}
\item \cref{cha:prerequisites} gives to the reader all the necessary notions
  to understand the rest of the chapter;
\item \cref{cha:scene} describes how the
  environment and the resulting curve are represented;
\item Finally in
\cref{cha:algorithm} we describe how to obtain the basic structures
(\cref{sec:polChain}), how to avoid the obstacles using the three
methods described before (\cref{sec:obsAvoid}), and how to improve the
obtained curve simplifying the control polygon (\cref{sec:postPro}),
increasing the curve degree (\cref{sec:degreeInc}) and changing the
\bs knot vector (\cref{sec:knotSel}).
\end{itemize}

The third part (\cref{prt:evaluation}) describes the instruments used
to implement the algorithms (cref{cha:codeStructure}) and presents
a series of tests with
different scenes and configurations (\cref{cha:testing}) with their
conclusions (\cref{cha:conclusions}).

In conclusion, \cref{cha:appendix} contains all the source code of the
application.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../dissertation"
%%% End:
